### 2018-01-27 Maths Notes/Mechanics/M2/Statics of rigid bodies/Statics of rigid bodies.tex
Notes Update

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{relsize}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}
\usepackage{tikz}
\usetikzlibrary{positioning}
\pgfplotsset{width=10cm,compat=1.9}

@@

\begin{document}
\begin{center}
\underline{\huge Kinematics}
\end{center}
\begin{obeylines}
\section{Horizontal Projections}
For a \textbf{constant speed} use \textbf{$Speed=\dfrac{Distance}{Time}$}

For a \textbf{constant acceleration} use \textbf{SUVAT}

For all projections:
\begin{itemize}
\item Assume air resistance to be zero
\item Resolve horizontal and vertical motion
\item Horizontal - Constant speed
\item Vertical - Constant acceleration

\end{itemize}

\section{Angular projections}
The same as horizontal projections but the initial vertical velocity isn't zero.
Example:
A particle is projected at a speed of $49ms^{-1}$ at an angle of $45 \degree$ above the horizontal.
\textit{What is the time taken for the particle to reach its maximum height?}
\begin{itemize}
\item u=$49\sin45$
\item v=0
\item a=-g
\item t=?
\end{itemize}
$0=49\sin45-gt$
$t=\dfrac{49\sin45}{g}=\dfrac{5\sqrt{2}}{2}\approx3.54$
\textit{What is the maximum height reached?}
\begin{itemize}
\item u=$49\sin45$
\item v=0
\item a=-g
\item s=?
\end{itemize}
$v^2=u^2+2as$
0=$(49\sin45)^2-2gs$
$S=\dfrac{(49\sin45)^2}{2g}=61.3$
\textit{What is the time of the flight?}
\begin{itemize}
\item u=$49\sin45$
\item a=-g
\item S=0
\item t=?
\end{itemize}
$S=ut+\dfrac{1}{2}at^2$
$ $
$0=(49\sin45)t-\dfrac{1}{2}gt^2$
0=$t(49\sin45-\dfrac{gt}{2}$
$t=0$
$49\sin45=\dfrac{gt}{2}$
$t=\dfrac{2\times49\sin45}{g}=7.07$
\textit{What is the horizontal range of the particle?}
\begin{itemize}
\item t=7.07
\item Speed=$49\cos45$
\end{itemize}
$S=45\cos45\times7.07=245$
\end{obeylines}
\section{Displacement, velocity and acceleration}
$v=\dfrac{dx}{dt}$\\
\\
$a=\dfrac{dv}{dt}$\\
\\
\begin{tikzpicture}
  \node (disp) {\textbf{Displacement} $x$};
  \node[right=2cm of disp] (vel) {\textbf{Velocity} $v$};
  \node[right=2cm of vel] (acc) {\textbf{Acceleration} $a$};
  \draw[-stealth,shorten >= 2pt] (disp.north) to[bend left] node[midway,above] {Differentiate} (vel.north);
  \draw[-stealth] (vel.south) to[bend left] node[midway,below] {Integrate} (disp.south);
  \draw[-stealth,shorten >= 2pt] (vel.north) to[bend left] node[midway,above] {Differentiate} (acc.north);
    \draw[-stealth] (acc.south) to[bend left] node[midway,below] {Integrate} (vel.south);
\end{tikzpicture}
\newpage
\begin{center}
\underline{\huge Kinematics Example - Problems with calculus}
\end{center}
\textit{A particle P moves along the x-axis in a straight line so that, at time t seconds, the velocity of P is $v \ \text{ms}^{-1}$, where}\\
\\
$
  v=\left\{
  \begin{array}{@{}ll@{}}
    10t-2t^2, & \text{for}\ 0\leqslant t \leqslant 6  \\
    -\dfrac{432}{t^2}, & t>6
  \end{array}\right.
$\\
\\
\\
\textit{At $t = 0$, P is at the origin O. Find the displacement of P from O when}\\
\\
$\mathit{t = 6}$\\
\\
\textbf{Integrate velocity}\\
\\
\textcolor{red}{$\mathlarger{x=\int v \ dt}$}\\
\\
$x=\int 10t-2t^2 \ dt= 5t^2-\frac{2}{3}t^3+c$\\
\\
\\
\textbf{Substitute in the value of t}\\
\\
$t=6$\\
\\
$x=5\times6^2-\frac{2}{3}\times6^3=36m$\\
\\
\\
$\mathit{t = 10}$
\\
\textbf{Integrate velocity for the second half of the journey}\\
\\
$x=\mathlarger{\int-\dfrac{432}{t^2} \ dt=\int-432t^{-2} \ dt=\dfrac{-432t^{-1}}{-1}+k=\dfrac{432}{t}+k}$\\
\\
\textbf{Find value of k by using known distance at t=6}\\
\\
$t=6 \ \ x=36$\\
\\
$36=\dfrac{432}{6}+k$\\
\\
$k=36-72=-36$\\
\\
\textbf{Find distance using value of k and t}\\
\\
$t=10$\\
\\
$x=\dfrac{432}{10}-36=7.2\text{m}$

>>>>

\documentclass{article}[18pt]
\usepackage[utf8]{inputenc}
\usepackage[margin=0.7in]{geometry}
\usepackage{parselines} 
\usepackage{amsmath}
\usepackage{titlesec}
\usepackage{pgfplots}
\usepackage{graphicx}
\usepackage[english]{babel}
\usepackage{fancyhdr}
\usepackage{gensymb}

\pgfplotsset{width=10cm,compat=1.9}

@@

\begin{document}
\begin{center}
\underline{\huge Statics of rigid bodies}
\end{center}
\section{Equilibrium of rigid bodies}
When calculating moments, only use the component of the force acting perpendicular to the rod.\\
\\
A rigid body is in equilibrium if:
\begin{itemize}
\item The vector sum of the forces is zero
\item The sum of the moments around any point is zero
\end{itemize}

### 2018-01-27 Maths Notes/Mechanics/M2/Work, energy and power/Work, energy and power.tex
Notes Update

\begin{document}
\begin{center}
\underline{\huge Kinematics}
\end{center}
\begin{obeylines}
\section{Horizontal Projections}
For a \textbf{constant speed} use \textbf{$Speed=\dfrac{Distance}{Time}$}

For a \textbf{constant acceleration} use \textbf{SUVAT}

For all projections:
\begin{itemize}
\item Assume air resistance to be zero
\item Resolve horizontal and vertical motion
\item Horizontal - Constant speed
\item Vertical - Constant acceleration

\end{itemize}

\section{Angular projections}
The same as horizontal projections but the initial vertical velocity isn't zero.
Example:
A particle is projected at a speed of $49ms^{-1}$ at an angle of $45 \degree$ above the horizontal.
\textit{What is the time taken for the particle to reach its maximum height?}
\begin{itemize}
\item u=$49\sin45$
\item v=0
\item a=-g
\item t=?
\end{itemize}
$0=49\sin45-gt$
$t=\dfrac{49\sin45}{g}=\dfrac{5\sqrt{2}}{2}\approx3.54$
\textit{What is the maximum height reached?}
\begin{itemize}
\item u=$49\sin45$
\item v=0
\item a=-g
\item s=?
\end{itemize}
$v^2=u^2+2as$
0=$(49\sin45)^2-2gs$
$S=\dfrac{(49\sin45)^2}{2g}=61.3$
\textit{What is the time of the flight?}
\begin{itemize}
\item u=$49\sin45$
\item a=-g
\item S=0
\item t=?
\end{itemize}
$S=ut+\dfrac{1}{2}at^2$
$ $
$0=(49\sin45)t-\dfrac{1}{2}gt^2$
0=$t(49\sin45-\dfrac{gt}{2}$
$t=0$
$49\sin45=\dfrac{gt}{2}$
$t=\dfrac{2\times49\sin45}{g}=7.07$
\textit{What is the horizontal range of the particle?}
\begin{itemize}
\item t=7.07
\item Speed=$49\cos45$
\end{itemize}
$S=45\cos45\times7.07=245$
\end{obeylines}
\section{Displacement, velocity and acceleration}
$v=\dfrac{dx}{dt}$\\
\\
$a=\dfrac{dv}{dt}$\\
\\
\begin{tikzpicture}
  \node (disp) {\textbf{Displacement} $x$};
  \node[right=2cm of disp] (vel) {\textbf{Velocity} $v$};
  \node[right=2cm of vel] (acc) {\textbf{Acceleration} $a$};
  \draw[-stealth,shorten >= 2pt] (disp.north) to[bend left] node[midway,above] {Differentiate} (vel.north);
  \draw[-stealth] (vel.south) to[bend left] node[midway,below] {Integrate} (disp.south);
  \draw[-stealth,shorten >= 2pt] (vel.north) to[bend left] node[midway,above] {Differentiate} (acc.north);
    \draw[-stealth] (acc.south) to[bend left] node[midway,below] {Integrate} (vel.south);
\end{tikzpicture}
\newpage
\begin{center}
\underline{\huge Kinematics Example - Problems with calculus}
\end{center}
\textit{A particle P moves along the x-axis in a straight line so that, at time t seconds, the velocity of P is $v \ \text{ms}^{-1}$, where}\\
\\
$
  v=\left\{
  \begin{array}{@{}ll@{}}
    10t-2t^2, & \text{for}\ 0\leqslant t \leqslant 6  \\
    -\dfrac{432}{t^2}, & t>6
  \end{array}\right.
$\\
\\
\\
\textit{At $t = 0$, P is at the origin O. Find the displacement of P from O when}\\
\\
$\mathit{t = 6}$\\
\\
\textbf{Integrate velocity}\\
\\
\textcolor{red}{$\mathlarger{x=\int v \ dt}$}\\
\\
$x=\int 10t-2t^2 \ dt= 5t^2-\frac{2}{3}t^3+c$\\
\\
\\
\textbf{Substitute in the value of t}\\
\\
$t=6$\\
\\
$x=5\times6^2-\frac{2}{3}\times6^3=36m$\\
\\
\\
$\mathit{t = 10}$
\\
\textbf{Integrate velocity for the second half of the journey}\\
\\
$x=\mathlarger{\int-\dfrac{432}{t^2} \ dt=\int-432t^{-2} \ dt=\dfrac{-432t^{-1}}{-1}+k=\dfrac{432}{t}+k}$\\
\\
\textbf{Find value of k by using known distance at t=6}\\
\\
$t=6 \ \ x=36$\\
\\
$36=\dfrac{432}{6}+k$\\
\\
$k=36-72=-36$\\
\\
\textbf{Find distance using value of k and t}\\
\\
$t=10$\\
\\
$x=\dfrac{432}{10}-36=7.2\text{m}$

\end{document}

>>>>

\begin{document}
\begin{center}
\underline{\huge Work, energy and power}
\end{center}
\begin{obeylines}
\section{Work}
$\mathbf{Work(J)=Force(N)\times Distance(m)}$
For work done against  gravity, use vertical distance.
For work against friction, use distance in the direction of motion
\section{Energy}
$\mathbf{E_K=\frac{1}{2}mv^2}$
$ $
$\mathbf{GPE=E_P=mgh}$
\section{Conservation of energy}
A particle's total energy is constant if it is subject only to gravity (i.e. smooth surfaces)
If there are frictional forces to consider then the loss of energy is the work done by friction.
\section{Power}
$\mathbf{Power=Force\times Velocity}$
Usually given in kW
\end{obeylines}
\end{document}
